\label{sec:INTRO}

Photography works by capturing different light intensities of a frame limited by the lens of the camera. Similarly, holographic technologies are able to capture the intensity and phase of the light being reflected off a 3D surface. This phase can be seen as extra information about the object and therefore gives the illusion of depth when the hologram is generated. In a similar way, it is possible to measure three dimensional depth by studding how a set of sinusoidal fringes deforms when projected onto a 3D geometry \cite{gaasvik2003optical}. The fringe deformations are encoded into the phase of the fringe pattern. By decrypting such phase, it is possible to measure the topography of the geometry being scanned. This techniques is known as Moiré by fringe displacement and its of of the many techniques studied by the field of optical metrology.  \\

This work aims to present a methodology that exploits Moire by fringe displacement to reconstruct a three dimensional bust using available market technology. The principal tools to implement this metrology are: a light source, a camera, a reference screen and of course; a computer. Furthermore, the team believes that with minor modifications to the methodology presented, this technology can have applications in the field of medical imaging, fashion industry, paleontology and archaeology \cite{Schofield:03}. Given that a person knows the technology and has access to the tools listed below; it is possible to obtain three dimensional measurements of a irregular geometry. Furthermore, these digital measurements can later be processed by computers including artificial intelligence algorithms. \\

Like any other technology, there are some limitations to what can be done with this technique of optical metrology. The considerations to this limitations are also exposed in the work. Thus, the purpose of this work is limited to understanding the key elements behind this technology to further propose upgrades, generalizations and concrete applications. To do so, the team scans and reconstructs computationally an interesting geometrical object. \\
